Probabilistic Forecasts in Hierarchical Time Series

### 2018-02-01 Probabilistic forecasts in hierarchical time series.tex
Draft 1

\documentclass[a4paper, 11pt]{article}
\usepackage[a4paper, inner=3cm, outer=3cm, top=2cm, bottom=3cm]{geometry}
\usepackage{amsmath, amssymb, fixmath, qtree, bm, calrsfs, enumitem,multirow, caption, textcmds,siunitx,adjustbox, mathrsfs, float, amstext}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usepackage[natbib=true,backend=bibtex,style=authoryear-comp,dashed=false,maxbibnames=99,firstinits=true,maxcitenames=3,url=true,doi=false,isbn=false]{biblatex}
\usepackage[pdftex,colorlinks=true]{hyperref}
\hypersetup{citecolor=blue,linkcolor=blue,urlcolor=blue}
\DeclareNameAlias{sortname}{last-first}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type

@@

\section{Introduction.}
\begin{itemize}
	\item Introduction to hierarchical time series including a literature review in the context of point forecasts. 
	\item Importance of probabilistic forecasts in time series.
	\item Lack of attention in the context of probabilistic forecasts in hierarchical literature.

\end{itemize}

@@

\begin{equation}
\mathbold{y}_t = \mathbold{Sb}_t,
\end{equation}
where $\mathbold{S}$ is a $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold. Since this linear subspace is equivalent to the column space of $\bm{S}$, we denote it as $\mathscr{C}(\bm{S})$. Further the null space of $\bm{S}$ which is orthogonal to this linear subspace is denoted by $\mathscr{N}(\bm{S})$. 
To understand the notations clearly, consider the hierarchy given in Figure 1.\\

\begin{figure}
	\begin{center}
		\leaf{AA} \leaf{AB} \leaf{AC}
		\branch{3}{A}
		\leaf{BA} \leaf{BB}
		\branch{2}{B}
		\branch{2}{Tot}
		\qobitree
	\end{center}
	\caption{Two level hierarchical diagram}
\end{figure}
\noindent
In any hierarchy, the most aggregated level is termed as level 0, the second most aggregated level is termed as level 1 and so on. This example consists of two levels. At a particular time $t$, let $y_{T,t}$ denote the observation at level 0; $y_{A,t}, y_{B,t} $ denote observations at level 1; and $y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}$ denote observations at level 2. Then $\mathbold{y}_t = [y_{T,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}]^T$, \\$\mathbold{b}_t = [y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}]^T$, $m=7$, n=11$, $ and $$ \mathbold{S} = \begin{pmatrix} 1& 1 &1 &1 &1 \\ 1 &1 &1 & 0 &0 \\   0&0 &0 & 1 & 1 \\ & & I_5 &  & \end{pmatrix}, $$ where $I_5$ is a $5$-dimension identity matrix. \\

@@

		\end{tikzpicture}
		\newline
	\end{center}
	\caption{Any set $\bm{A} \in \bm{\mathbb{R}}$ will be mapped to the $\mathscr{C}(\bm{S})$ through the mapping $\bm{S}$}
\end{figure}
\noindent
Definition 3.2 implies the probability measure on $\mathscr{C}(\bm{S})$ is equivalent to the probability measure on $(\bm{\mathbb{R}}^m, \bm{\mathscr{F}}^m)$. Hence, there is no density anywhere outside the linear subspace spanned by the columns of $\bm{S}$. That is, a \textit{Coherent probability density forecast} is any density $\bm{f}(\bm{\breve{y}}_{t+h})$ such that $\bm{f}(\bm{\breve{y}}_{t+h})=0$ for all $\bm{\breve{y}}_{t+h}$ in the null space of $\bm{S}$. Following example will help to understand these definitions more clearly.\\

@@

\noindent
By the definition of coherent forecasts, it is clear that there are only $m$ number of linear independent series in the whole hierarchy. We refer to these as $m$ dimensional \textit{basis set of series} since these series generates a \textit{basis} that spans the $\mathscr{C}(\bm{S})$. Other $n-m$ series of the hierarchy can be linearly determined by these basis set of series. This implies that any coherent density is a degenerate density. The $m$ number of bottom level series of a given hierarchy can be considered as a basis set of series. Then the columns of $\bm{S}$ is a basis that generates through these bottom level series. This basis spans the linear subspace where the degenerate density lives on.\\

@@

\noindent
It is also worth to mention that the definition $(3.1)$ and $(3.2)$ facilitate extension to the forecast reconciliation which we talk about in the next section. In contrast to our definition, \citet{BenTaieb2017} defines the coherent probabilistic forecasts in terms of convolution. According to their definition, if the forecasts are coherent, then the convolution of forecast distributions of disaggregate series is same as the forecast distribution of the corresponding aggregate series. This is the only study that copes with probabilistic forecasts in hierarchical literature thus far.

\section{Forecast reconciliation}
\noindent
Bottom-up, top-down and middle-out methods are the most traditional forecasting methods that were used to produce coherent point forecasts in early studies on hierarchical literature. In bottom-up approach, forecasts of the lowest level are first generated and they are simply aggregated to forecast the upper levels of the hierarchy \citep{Dunn1976}. 
In contrast, the top-down approach involves forecasting the most aggregated series first and then disaggregating these forecasts down the hierarchy based on the proportions of observed data \citep{Gross1990}. A compromise between these two approaches is the middle-out method which entails forecasting each series of a selected middle level in the hierarchy and then forecasting upper levels by the bottom-up method and lower levels by the top-down method.\\

\noindent
These three approaches use only a part of the information available when producing coherent forecasts. This might result inaccurate forecasts. For example, if the bottom level series are highly volatile or too noisy and hence challenging to forecast, then the resulting forecasts from bottom-up approach would be inaccurate.\\

\noindent
As an alternative to these conventional methods, \citet{Hyndman2011} propose to use information from all the levels of the hierarchy and reconcile them to obtain coherent point forecasts. In this approach, independent forecasts of all series are initially obtained. It is very unlikely that these forecasts are coherent. Then, these forecasts are optimally combined through a regression model to obtain coherent forecasts. This study has given arise to the concept of point forecast reconciliation in hierarchical time series. In general, any forecasting method that use a set of incoherent forecasts and revise them to obtain coherent forecasts is referred to as forecast reconciliation method. For example, Minimum Trace reconciliation \citep{Wickramasuriya2017}, GTOP \citep{VanErven2015a}. It is important to notice that bottom-up, top-down and middle-out methods are not reconciliation methods since they only use forecasts from a part of the levels in the hierarchy when producing coherent forecasts. \\

@@

Even though the point forecast reconciliation has a well established literature, we would like to redefine this using concepts in linear algebra as a groundwork for the probabilistic forecast reconciliation. \\

@@

\noindent
Finding a suitable $\bm{R}_\bot$ with respect to a certain loss function will result optimally reconciled point forecasts of the hierarchy. Notice that, if the mapping $\bm{g}$ in definition 4.1 is considered to be linear we have,
\begin{flalign}
\bm{g}=(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot.
\end{flalign}
\noindent
In previous studies on hierarchical point forecasting, $\bm{g}$ is considered as a $m \times n$ matrix $\bm{P}$ and thus $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$. 
In other words, $\bm{g}$ linearly projects incoherent point forecasts onto the $\mathscr{C}(\bm{S})$. Further in our context, we need to find $\bm{R}_\bot$ such that $\bm{R}^T_\bot \bm{S}$ is invertible. i.e, $(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot \bm{S}=\bm{I}$. This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}.

@@

\noindent
According to a recent study by \citet{Wickramasuriya2017}, choosing $\bm{R}^T_\bot = \bm{S}^T\hat{\bm{W}}^{-1}_{T+h}$ will minimize the trace of mean squared reconciled forecasts errors under the property of unbiasedness. $\hat{\bm{W}}^{-1}_{T+h}$ is the variance of the incoherent forecast errors. This will result, 
\begin{flalign*}
\tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}^T\hat{\bm{W}}^{-1}_{T+h} \bm{S})^{-1}\bm{S}^T\hat{\bm{W}}^{-1}_{T+h} \hat{\bm{y}}_{t+h},
\end{flalign*}
and thus,
\begin{flalign}
\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}^T \hat{\bm{W}}^{-1}_{T+h}\bm{S})^{-1}\bm{S}^T\hat{\bm{W}}^{-1}_{T+h} \hat{\bm{y}}_{t+h}.
\end{flalign}

\noindent
They referred this to as MinT solution. It is also worth to notice that the loss function they considered is equivalent to the Mahalanobis distance between $\hat{\bm{y}}_{T+h}$ and $\tilde{\bm{y}}_{T+h}$. i.e. $<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>_{\hat{\bm{W}}}$.

@@

\noindent  
Suppose $\hat{\bm{Y}}_{t+h} \sim \mathscr{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h}) \leftrightarrow^d \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$. Then from (\ref{4.5}) it follows,

@@

\begin{flalign*}
\bm{f_B}(.)&=\frac{\exp\left\{-\frac{1}{2}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})^T \bm{\hat{\Sigma}_{t+h}}^{-1}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
&= \frac{\exp\left\{-\frac{1}{2}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\bm{\hat{\mu}}_{t+h}\Big)^T \bm{\hat{\Sigma}_{t+h}}^{-1}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
\end{flalign*}

\begin{flalign*}
\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|}
\exp \Big\{&-\frac{1}{2}\Big(\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big)^T\\
&\Big[\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^T\Big]^{-1}\\ 
&\Big(\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.
\end{flalign*}
\noindent
Recall that, $$\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot\\ \cdots \\ (\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot
\end{pmatrix} = \begin{pmatrix}
\bm{P}\\\bm{Q}
\end{pmatrix},$$ where, $\bm{P}=(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$ and $\bm{Q}=(\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot$. Then,

@@

		}
\end{center}
\textit{NOTE: $\bm{\breve{Y}}_{T+h}$ and $\bm{\breve{Y}}'_{T+h}$ be two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with the density function $\breve{\bm{f}}(.)$ at time $t+h$ and $\bm{y}_{T+h}$ is the vector of realizations. Further $\breve{Y}_{T+h,i}$ and $\breve{Y}_{T+h,j}$ are $i^{\text{th}}$ and $j^{\text{th}}$ components of the vector $\breve{\bm{Y}}_{T+h}$. Further the variogram score given is for order $p$ where, $w_{ij}$ are non-negative weights.}\\

@@

\noindent
However we could compare individual margins of the forecast density of the hierarchy using univariate proper scoring rules. Most widely used Continuous Ranked Probability Score (CRPS) for evaluating univariate forecast densities would be helpful for this. \\

\begin{equation} \label{eq:(3.6)}
CRPS(\breve{F}_i,y_{T+h,i}) = E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}'_{T+h,i}|,
\end{equation}

\noindent
where $\breve{Y}_{T+h,i}$ and $\breve{Y}'_{T+h,i}$ are two independent copies from the $i^{\text{th}}$ reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy and $y_{T+h,i}$ is the $i^{\text{th}}$ realization from the true marginal distribution $G_i$.

\subsection{Simulation study}

>>>>

\documentclass[a4paper, 11pt]{article}
\usepackage[a4paper, inner=3cm, outer=3cm, top=2cm, bottom=3cm]{geometry}
\usepackage{amsmath, amssymb, fixmath, qtree, bm, calrsfs, enumitem,multirow, caption, textcmds,siunitx,adjustbox, mathrsfs, float, amstext}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usepackage[natbib=true,backend=bibtex,style=authoryear-comp,dashed=false,maxbibnames=99,firstinits=true,maxcitenames=3,url=true,doi=false,isbn=false]{biblatex}
\usepackage[pdftex,colorlinks=true]{hyperref}
\hypersetup{citecolor=blue,linkcolor=blue,urlcolor=blue}
\DeclareNameAlias{sortname}{last-first}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type
\def\mathbi#1{\textit{ #1}}
\def\mathB#1{\textbf{ #1}}

@@

\section{Introduction.}
Many research applications often involve a large collection of multiple time series some of which are aggregates of others.
These collection of time series are called hierarchical time series. For example, electricity demand of a country can be disaggregated along a geographical hierarchy. One would be interested in forecasting electricity demand of the whole country along with the demand of states, cities and households. This is referred to as hierarchical forecasting. An important aspect of hierarchical forecasting is to have coherent forecasts across the hierarchy; that is, forecasts at lower levels should add up to their respective upper levels of aggregation.\\

\noindent
There is a rich literature on producing coherent point forecasts in hierarchical time series. The traditional approaches involve bottom-up, top-down and middle-out methods. In the bottom-up approach, forecasts of the lowest level are first generated and they are simply aggregated to forecast upper levels of the hierarchy \citep{Dunn1976}.  
In contrast, the top-down approach involves forecasting the most aggregated series first and then disaggregating these forecasts down the hierarchy based on the proportions of observed data \citep{Gross1990}. 
Many studies in the literature have broadly discussed the relative advantages and disadvantages of bottom-up and top-down methods and situations in which they would provide reliable forecasts \citep{Schwarzkopf1988,Kahn1998, Lapide1998,Fliedner2001}.
A compromise between these two approaches is the middle-out method which entails forecasting each series of a selected middle level in the hierarchy and then forecasting upper levels by the bottom-up method and lower levels by the top-down method. Apparently, these three approaches use only a part of the information available when producing coherent forecasts. This might result inaccurate forecasts. For example, if the bottom level series are highly volatile or too noisy and hence challenging to forecast, then the resulting forecasts from bottom-up approach would be inaccurate.\\

\noindent
As an alternative to these conventional methods, \citet{Hyndman2011} propose to use information from all the levels of the hierarchy and reconcile them to obtain coherent point forecasts. In this approach, independent forecasts of all series are initially obtained. It is very unlikely that these forecasts are coherent. Then, these forecasts are optimally combined through a regression model to obtain coherent forecasts. This study has given arise to the concept of point forecast reconciliation in hierarchical time series. In general, any forecasting method that use a set of incoherent forecasts and revise them to obtain coherent forecasts is referred to as forecast reconciliation method. Thus it is important to notice that bottom-up, top-down and middle-out methods are not reconciliation methods since they use only a part of information from the hierarchy to produce coherent forecasts. \\

\noindent
In a recent study on point forecast reconciliation, \citet{Wickramasuriya2017} propose to minimize the trace of mean squared coherent forecasts errors to optimally reconcile a set of unbiased, incoherent forecasts. Assuring the resulting reconciled forecasts are unbiased, they found an unique analytical solution to the proposed minimization problem. They referred this to as MinT approach. This solution was further improved to be computationally feasible for high dimensional hierarchies. \\

\noindent
In recent forecasting literature, its being the rationality to provide the associated uncertainty about the future, in addition to the point forecasts. This is referred to as probabilistic forecasts \citep{Gneiting2014}. For example, \citet{McSharry2005} produced probabilistic forecasts in application to electricity demand, \citet{BenTaieb2017} in application to smart meter data, \citet{Pinson2009} in application to wind power generation, \citet{Gel2004}, \citet{Gneiting2005a} and \citet{Gneiting2005} in application to prediction of weather quantities. \\

\noindent      
Although there is a thorough literature on producing coherent point forecasts of hierarchical time series, a very limited attention has been given in the context on probabilistic forecasts. Recently \citet{BenTaieb2017} proposed an algorithm to produce coherent probabilistic forecasts with the application to UK electricity smart meter data. This is the only study that copes with the probabilistic forecasts in hierarchical time series thus far. In their approach, a sample from the mean reconciled predictive distribution of the bottom level will be first generated. This sample will be then aggregated to obtain the coherent probabilistic forecasts of the respective upper levels of the hierarchy. Hence this method is a bottom-up based approach. They further use MinT approach for the mean reconciliation of the bottom level predictive distribution and a copula based approach to model the dependency structure of the hierarchy, when producing the sample of bottom level probabilistic forecasts.\\

\noindent
Our contribution in this paper is to provide a proper theoretical background for the probabilistic hierarchical forecasts. First we redefine the coherency of point forecasts and the reconciliation of a set of incoherent point forecasts by using the concepts on vector spaces and measure theory. This will leads us to provide a proper definition for probabilistic forecast reconciliation. Due to the aggregation structure in hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate. We discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation and also in the evaluation of their predictive performances. Further we provide theoretical results on probabilistic forecast reconciliation in the Gaussian framework. \\

\noindent
Rest of the paper is structured as follows. We start with introducing the notations in section 2. In section 3 we provide our definitions for coherency which is followed by the definitions for forecast reconciliation in section 4. Section 5 discuss about the methods that can be used for evaluation of probabilistic hierarchical forecasts. Section 6 consists the theoretical results followed by the simulation study on probabilistic forecast reconciliation in Gaussian framework and we enclose with the remarkable conclusions in section 7.

@@

\begin{equation}
\mathbold{y}_t = \mathbold{Sb}_t,
\end{equation}
where $\mathbold{S}$ is a $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold. Since this linear subspace is equivalent to the column space of $\bm{S}$, we denote it as $\mathscr{C}(\bm{S})$. Further the null space of $\bm{S}$ which is orthogonal to this linear subspace is denoted by $\mathscr{N}(\bm{S})$. 
To understand the notations clearly, consider the hierarchy given in Figure 1.
\begin{figure}[H]
	\begin{center}
		\leaf{AA} \leaf{AB} 
		\branch{2}{A}
		\leaf{BA} \leaf{BB}
		\branch{2}{B}
		\branch{2}{Tot}
		\qobitree
	\end{center}
	\caption{Two level hierarchical diagram}
\end{figure}
\noindent
In any hierarchy, the most aggregated level is termed as level 0, the second most aggregated level is termed as level 1 and so on. This example consists of two levels. At a particular time $t$, let $y_{Tot,t}$ denote the observation at level 0; $y_{A,t}, y_{B,t} $ denote observations at level 1; and $y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}$ denote observations at level 2. Then $\mathbold{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}]^T$, \\$\mathbold{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]^T$, $m=4$, $n=7$, and $$ \mathbold{S} = \begin{pmatrix} 1& 1 &1 &1  \\ 1 &1 & 0 &0 \\   0&0  & 1 & 1 \\ & & I_4 &   \end{pmatrix}, $$ where $I_4$ is a $4$-dimension identity matrix. \\

@@

		\end{tikzpicture}
		\newline
	\end{center}
	\caption{Any set $\bm{A} \in \bm{\mathbb{R}}^m$ will be mapped to the $\mathscr{C}(\bm{S})$ through the mapping $\bm{S}$}
\end{figure}
\noindent
Definition 3.2 implies the probability measure on $\mathscr{C}(\bm{S})$ is equivalent to the probability measure on $(\bm{\mathbb{R}}^m, \bm{\mathscr{F}}^m)$. Hence, there is no density anywhere outside the linear subspace spanned by the columns of $\bm{S}$. That is, a \textit{Coherent probability density forecast} is any density $\bm{f}(\bm{\breve{y}}_{t+h})$ such that $\bm{f}(\bm{\breve{y}}_{t+h})=0$ for all $\bm{\breve{y}}_{t+h}$ in the null space of $\bm{S}$. Following example will help to understand these definitions more clearly.\\

@@

\noindent
By the definition of coherent forecasts, it is clear that there are only $m$ number of linear independent series in the whole hierarchy. We refer to these as $m$ dimensional \textit{basis set of series} since these series generates a \textit{basis} that spans the $\mathscr{C}(\bm{S})$. Other $n-m$ series of the hierarchy can be linearly determined by these basis set of series. This implies that any coherent density is a degenerate density. In particular, the $m$ number of bottom level series of a given hierarchy can be considered as a basis set of series. Then the columns of $\bm{S}$ is a basis that generates through these bottom level series. This basis spans the linear subspace where the degenerate density lives on.\\

@@

\noindent
It is also worth to mention that the definition $(3.1)$ and $(3.2)$ facilitate extension to the forecast reconciliation which we talk about in the next section. In contrast to our definition, \citet{BenTaieb2017} defines the coherent probabilistic forecasts in terms of convolution. According to their definition, if the forecasts are coherent, then the convolution of forecast distributions of disaggregate series is same as the forecast distribution of the corresponding aggregate series.

\section{Forecast reconciliation}

Previous studies on point forecast literature has shown that the reconciliation provides better coherent forecasts than the conventional bottom-up and top-down methods (\cite{Hyndman2011}; \cite{VanErven2015a}; \cite{Wickramasuriya2017}). However this was not well established in the context of probabilistic forecasts. Nevertheless, there is no proper definition for the probabilistic forecast reconciliation in the published literature. Thus in this section we focus on defining the probabilistic forecast reconciliation and discuss how that definition can be used in practice.

@@

Initially we redefine point forecast reconciliation using the concepts in linear algebra as a groundwork for the probabilistic forecast reconciliation. \\

@@

\noindent
Finding a suitable $\bm{R}_\bot$ with respect to a certain loss function will result optimally reconciled point forecasts of the hierarchy. Notice that, if the mapping $\bm{g}$ in definition 4.1 is considered to be linear we have,
\begin{flalign}
\bm{g}=(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot.
\end{flalign}
\noindent
In previous studies on hierarchical point forecasting, $\bm{g}$ is considered as a $m \times n$ matrix $\bm{P}$ and thus $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$. 
In other words, $\bm{g}$ linearly projects incoherent point forecasts onto the $\mathscr{C}(\bm{S})$. Further in our context, we need to find $\bm{R}_\bot$ such that $\bm{R}^T_\bot \bm{S}$ is invertible. i.e, $(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot \bm{S}=\bm{I}$. This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}. \\

@@

\noindent
According to a recent study by \citet{Wickramasuriya2017}, choosing $\bm{R}^T_\bot = \bm{S}^T\bm{W}^{-1}_{h}$ will minimize the trace of mean squared reconciled forecasts errors under the property of unbiasedness where, $\bm{W}^{-1}_{h}$ is the variance of the incoherent forecast errors. This will result, 
\begin{flalign*}
\tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}^T\bm{W}^{-1}_{h} \bm{S})^{-1}\bm{S}^T\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h},
\end{flalign*}
and thus,
\begin{flalign}
\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}^T \bm{W}^{-1}_{h}\bm{S})^{-1}\bm{S}^T\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h}.
\end{flalign}

\noindent
They referred this to as MinT solution. It is also worth to notice that the loss function they considered is equivalent to the Mahalanobis distance between $\hat{\bm{y}}_{T+h}$ and $\tilde{\bm{y}}_{T+h}$. i.e. $<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>_{\bm{W}_h}$.

@@

\noindent  
Suppose $\mathscr{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h})\leftrightarrow^d \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ is an incoherent forecast distribution at time $t+h$. Then from (\ref{4.5}) it follows,

@@

\begin{flalign*}
\bm{f_B}(.)&=\frac{\exp\left\{-\frac{1}{2}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})^T \bm{\hat{\Sigma}_{t+h}}^{-1}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
&= \frac{\exp\left\{-\frac{1}{2}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)^T \bm{\hat{\Sigma}_{t+h}}^{-1}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
\end{flalign*}

\begin{flalign*}
\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|}
\exp \Big\{&-\frac{1}{2}\Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big)^T\\
&\Big[\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^T\Big]^{-1}\\ 
&\Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.
\end{flalign*}
\noindent
Recall that, $$\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot\\ \cdots \\ (\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot
\end{pmatrix} = \begin{pmatrix}
\bm{P}\\\bm{Q}
\end{pmatrix},$$ where, $\bm{P}=(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$ and $\bm{Q}=(\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot$. Then,

@@

		}
\end{center}
\textit{NOTE: $\bm{\breve{Y}}_{T+h}$ and $\bm{\breve{Y}}'_{T+h}$ be two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with the density function $\breve{\bm{f}}(.)$ at time $T+h$ and $\bm{y}_{T+h}$ is the vector of realizations. Further $\breve{Y}_{T+h,i}$ and $\breve{Y}_{T+h,j}$ are $i^{\text{th}}$ and $j^{\text{th}}$ components of the vector $\breve{\bm{Y}}_{T+h}$. Further the variogram score given is for order $p$ where, $w_{ij}$ are non-negative weights.}\\

@@

\noindent
However we could compare individual margins of the forecast density of the hierarchy using univariate proper scoring rules. Most widely used Continuous Ranked Probability Score (CRPS) for evaluating univariate forecast densities would be helpful for this. \\
\begin{equation} \label{eq:(3.6)}
CRPS(\breve{F}_i,y_{T+h,i}) = E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}'_{T+h,i}|,
\end{equation}

\noindent
where $\breve{Y}_{T+h,i}$ and $\breve{Y}'_{T+h,i}$ are two independent copies from the $i^{\text{th}}$ reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy and $y_{T+h,i}$ is the $i^{\text{th}}$ realization from the true marginal distribution $G_i$. We can also use univariate log scores for which we could assume a parametric forecast distribution.

\section{Probabilistic forecast reconciliation in the Gaussian framework}

Main purpose of this section is to establish the importance of reconciliation in probabilistic hierarchical forecasting. We narrow down the simulation setting for the Gaussian framework in this work. That is, suppose all the historical data in the hierarchy follows a multivariate Gaussian distribution, i.e. $\bm{y}_T \sim \mathscr{N}(\bm{\mu}_T, \bm{\Sigma}_T)$ where both $\bm{\mu}_T$ and $\bm{\Sigma}_T$ lives in $\mathscr{C}(\bm{S})$ by nature of the hierarchical time series. We are interested in estimating the predictive Gaussian distribution of $\bm{Y}_{T+h}| \bm{\mathcal{I}}_T$ where $\bm{\mathcal{I}}_T= \{\bm{y}_1,\bm{y}_2,....,\bm{y}_T\}$, which should also lives in $\mathscr{C}(\bm{S})$. \\

\noindent
Suppose we independently fit the models for each series in the hierarchy. Let $\hat{Y}_{T+h,i}$ gives the point forecast of $i^{\text{th}}$ series at time $T+h$ conditional on the past observations $\{y_{1,i},...,y_{T,i}\}$ which minimizes the mean squared forecast error of $Y_{T+h,i}|\{y_{1,i},...,y_{T,i}\}$, where $i=1,...,n$. Then we have, $$\hat{Y}_{T+h,i} = E[Y_{T+h,i}|y_{1,i},...,y_{T,i}]$$

\noindent
Let $\hat{\bm{Y}}_{T+h}=(\hat{Y}_{T+h,1},...,\hat{Y}_{T+h,n})'$. Then, $$\hat{\bm{\mu}}_{T+h}=E[\bm{Y}_{T+h}|\bm{\mathcal{I}}_T] = \hat{\bm{Y}}_{T+h}.$$
